---
title: "Looking for continuative markers in potential continuative contexts"
---

```{r}
library(tidyverse)
library(lingtypology)
```

load the data

```{r}
df <- read.csv("sample.csv")
df %>%
  filter(included != "no") -> df1
df1
```
choose markers only in those languages which have translations of the Gospel of Luke (in R. Östling's corpus)
markers which I did not manage to find in translations are also not included

```{r}
df1 %>%
  filter(form_in_Bible != "(not found)" & 
           form_in_Bible != "(no Bible)" & 
           form_in_Bible != "(Bible not from corpus)") %>%
  select ("id_number", "family", "iso", "language", "form", "form_in_Bible", "Bible") -> df2
df2
```

create a list of commands which run find_instances.py for each of the markers
find_instances.py can be found here: https://github.com/robertostling/parallel-tools


```{r}
file.create("commands_for_searching_continuative_markers.sh")
for (x in df2$form_in_Bible) {
  command = paste("python3 /Users/apanova/OneDrive/Documents/Continuative/Continuative_Bibles/parallel-tools-master/find_instances.py -e '", x, "' /Users/apanova/Downloads/corpus/", df2$Bible[df2$form_in_Bible == x], " > results/", df2$iso[df2$form_in_Bible == x], "_", df2$id_number[df2$form_in_Bible == x], ".txt", sep = "", collapse = NULL)
  write(command,file="commands_for_searching_continuative_markers.sh",append=TRUE)
}
```

#######

HERE YOU NEED TO DO THE FOLLOWING:

COPY COMMANDS FROM SH FILE AND RUN IT FROM BASH
SOME COMMANDS PRODUCE EMPTY FILES IN THE RESULTS DIRECTORY (I DO NOT KNOW WHY)
FIND THEM AND RUN COMMANDS FOR PRODUCING THESE FILES SEPARATELY ONE BY ONE (THIS WAY THEY USUALLY WORK)

#######

get the full list of files and save it

```{r}
try(system("ls results > list_of_files_with_results.txt", ignore.stderr = TRUE))
```

```{r}
list_of_files <- read.csv("list_of_files_with_results.txt", header = FALSE)
list_of_files
```

run the python script which selects lines with results for the Gospel of Luke and saves numbers of verses with continuative markers in a csv

```{r}
try(system("python3 select_numbers_of_verses_with_continuatives_in_Luke.py"))
```

load csv

```{r}
contexts_with_continuatives <- read.csv("contexts_with_continuatives.csv", header = FALSE, sep = "\t")
contexts_with_continuatives
```
transform the data into a more user-friendly format

```{r}
contexts_with_continuatives %>%
  separate_rows(V2, sep = ", ") %>%
  filter(V2 != "") %>%
  mutate(tf = 1) %>%
  spread(V2, tf, fill = 0) %>%
  separate(V1, c('iso_code', 'id_number')) -> contexts_with_continuatives_table
contexts_with_continuatives_table
```
save the data on contexts with continuative markers

```{r}
write.csv(contexts_with_continuatives_table,file="contexts_with_continuatives_table.csv")
```

create a variable with the list of potentially continuative contexts in the Gospel of Luke (identified based on the manual semantic analysis of the text)


```{r}
potentially_continuative_contexts = c("42008049", "42009034", "42009042", "42009043", "42012058", "42014022", "42014032", "42015020", "42018022", "42019033", "42022047", "42022060", "42024006", "42024041", "42024044", "42024051")
```

add data on occurrences of continuative markers in Abaza, Lezgian and Gban translations of the Gospel of Luke (which are not from the corpus)

```{r}
contexts_with_continuatives_table %>%
  select("iso_code", "id_number", potentially_continuative_contexts) %>%
  add_row(iso_code ="abq", "id_number" = "25", "42008049" = 0, 
          "42009034" = 0, "42009042" = 0, "42009043" = 0, "42012058" = 0, 
          "42014022" = 1, "42014032" = 0, "42015020" = 0, "42018022" = 1, 
          "42019033" = 0, "42022047" = 0, "42022060" = 0, "42024006" = 0, 
          "42024041" = 0, "42024044" = 0, "42024051" = 0) %>%
  add_row(iso_code ="abq", "id_number" = "24", "42008049" = 1, 
          "42009034" = 1, "42009042" = 0, "42009043" = 0, "42012058" = 1, 
          "42014022" = 0, "42014032" = 1, "42015020" = 1, "42018022" = 0, 
          "42019033" = 0, "42022047" = 1, "42022060" = 1, "42024006" = 1, 
          "42024041" = 0, "42024044" = 1, "42024051" = 0) %>%
  add_row(iso_code ="lez", "id_number" = "15", "42008049" = 1, 
          "42009034" = 0, "42009042" = 0, "42009043" = 1, "42012058" = 1, 
          "42014022" = 1, "42014032" = 1, "42015020" = 1, "42018022" = 0, 
          "42019033" = 0, "42022047" = 1, "42022060" = 0, "42024006" = 0, 
          "42024041" = 0, "42024044" = 1, "42024051" = 0) %>%
  add_row(iso_code ="lez", "id_number" = "16", "42008049" = 0, 
          "42009034" = 0, "42009042" = 0, "42009043" = 0, "42012058" = 0, 
          "42014022" = 0, "42014032" = 0, "42015020" = 1, "42018022" = 0, 
          "42019033" = 0, "42022047" = 0, "42022060" = 0, "42024006" = 0, 
          "42024041" = 1, "42024044" = 1, "42024051" = 0) %>%
  add_row(iso_code ="ggu", "id_number" = "48", "42008049" = 1, 
          "42009034" = 1, "42009042" = 0, "42009043" = 0, "42012058" = 1, 
          "42014022" = 0, "42014032" = 0, "42015020" = 1, "42018022" = 0, 
          "42019033" = 1, "42022047" = 1, "42022060" = 1, "42024006" = 0, 
          "42024041" = 1, "42024044" = 1, "42024051" = 0) %>%
  add_row(iso_code ="ggu", "id_number" = "49", "42008049" = 0, 
          "42009034" = 0, "42009042" = 0, "42009043" = 0, "42012058" = 0, 
          "42014022" = 0, "42014032" = 0, "42015020" = 0, "42018022" = 0, 
          "42019033" = 0, "42022047" = 0, "42022060" = 0, "42024006" = 0, 
          "42024041" = 0, "42024044" = 0, "42024051" = 0) -> continuative_contexts_with_add_langs
continuative_contexts_with_add_langs
```

save full data as csv

```{r}
write.csv(continuative_contexts_with_add_langs,file="continuative_contexts_with_add_langs.csv")
```


calculate the sum of occurrences in the continuative contexts for each continuative marker

```{r}
continuative_contexts_with_add_langs$sum <- rowSums(continuative_contexts_with_add_langs[,3:18])
continuative_contexts_with_add_langs %>%
  select ("iso_code", "id_number", "sum") -> numbers_of_occurrences_in_cnt_contexts
numbers_of_occurrences_in_cnt_contexts
```

to draw a map, choose only one marker for each language, i.e. in case of doubling of iso_code, exclude the marker with lower frequency


```{r}
numbers_of_occurrences_in_cnt_contexts %>%
  subset(id_number != "23" & id_number != "2" & id_number != "67" &
           id_number != "25" & id_number != "16" & id_number != "49") -> numbers_of_occurrences_in_cnt_contexts_for_map
numbers_of_occurrences_in_cnt_contexts_for_map
```

```{r}
map.feature(languages = lang.iso(numbers_of_occurrences_in_cnt_contexts_for_map$iso_code),
            features = as.numeric(numbers_of_occurrences_in_cnt_contexts_for_map$sum))
```

